\documentclass[10pt]{report}
\usepackage{graphicx}
\usepackage{a4}
\usepackage{url}
\usepackage{fullpage}

% Report template authored V. Sorge, adapted S. Vickers.

\title{% This is the title of your document
{\normalsize Software Workshop Team Java (06-08165) 2010/11, Dr. E. Thompson}\\[2cm]
Project Report:\\
Space Runner Game}
\author{Team B3:\\
Daniel Cecil\\
Jere Ketonen\\
David Saunders\\
Michal Staniaszek
}

\begin{document}
\maketitle
\chapter*{Work Breakdown}
\label{work-breakdown}

\thispagestyle{empty}

% Obviously these need discussing and changing....
{\small

\noindent\begin{tabular}{|l||l|l|l|l|l|}\hline
  \textbf{Coding} & \textbf{Daniel} & \textbf{Jere} & \textbf{David}
 & \textbf{Michal} \\\hline\hline
 Datastructures & Contribution: 100\% & 0\% & 0\% & 0\%\\\hline
 \ldots & \ldots & \ldots & \ldots & \ldots \\\hline
\end{tabular}\vspace*{1cm}

\noindent\begin{tabular}{|l||l|l|l|l|l|}\hline
  \textbf{Report} & \textbf{Daniel} & \textbf{Jere} & \textbf{David}
 & \textbf{Michal}\\\hline\hline
 Introduction & Chapter~\ref{cha:introduction}: 100\% & 0\% & 0\% & 0\%\\\hline
 \ldots & \ldots & \ldots & \ldots & \ldots \\\hline
\end{tabular}

}     % This is the "}" that matches the "{" before "\small"

\tableofcontents
\thispagestyle{empty}

\begin{abstract}
  You should write a one-page abstract written as an ``Executive Summary''. It
  should be written for someone who is familiar with the Team Java module, so
  that there is no need for background or generalities. Rather, you should
  explain what is special about your project, and what you claim to have
  achieved. (One page maximum.)
\end{abstract}

\include{introduction} % needs doing...
\include{requirements}
\include{design} % Dan to finish
\include{validation} % Michal
\include{management} % Jere
\include{conclusions}

\bibliographystyle{plain}
\bibliography{report}

Acknowledge any code you have used (if any), and also any that was
generated automatically, e.g. by wizards.

Give correct and complete bibliographic information for any sources
cited. See the local referencing guide. For instance cite which
books on software engineering you have used, for
instance~\cite{software-design}. Use the \texttt{report.bib} file to
manage your citations.

When you \emph{quote} material from other sources, you must be
absolutely clear \emph{at the point where you quote it} exactly
which of your material is quoted and what the source is. As
explained in \cite{SoCS:plagiarism},

``Direct quotation is not particularly common in scientific writing,
as it is generally not the words that matter, but the meaning.
Normally it is preferable to rewrite someone else's ideas in your
own words, often changing the terminology and other superficial
details to suit the new context.

However, in circumstances where it is appropriate to make direct use
of the words of another person, those words should normally be
included within quotation marks and a reference to the source of the
words given in the usual way.''

\end{document}
