\section{Team Java Work Log}
\label{app:worklog}
\begin{itemize}
\item \textbf{Week 1}
  \begin{itemize}
  \item \textbf{As a team} \\We met up together and compared
    timetables so we could work out the best times to meet. Once we
    had worked out that we did a quick brain storm of ideas together
    to see if any big ideas “jumped” out at us – 1 hour.  Since we had
    earlier decided that Thursday was fine for a team meeting with our
    tutor (Errol) we decided to contact him and ask if it is possible
    to have a meeting with him at some point.  On Thursday we met up
    with our tutor and discussed what ideas we had come up with in our
    first team meeting earlier in the week. We were then told to
    expand upon these ideas for the meeting next week and possibly
    have a better idea of what we were going to aim for.
  \item \textbf{Dxs970, Dwc928, mxs968, jkx988} \\We all did our own
    individual research on different game types and the benefits and
    drawbacks of each genre.
  \item \textbf{Dxs970} \\Typed up the notes we made during the week
  \end{itemize}
\item \textbf{Week 2}
  \begin{itemize}
  \item \textbf{As a group}\\
    Met up on Tuesday to continue discussions on ideas building upon
    the research we did last week. During the discussion we came to
    the conclusion we wanted something simple and easily to
    manipulate/change which led us towards the idea of doing a side
    scrolling space shooter. – 3 hours On Thursday we again met up
    with the tutor and talked over the ideas we had with him and how
    we were leaning towards going with a space shooter. He then gave
    us his opinion on what we told him and advice on how we could
    possibly do this. After this he then showed us how to use SVN
    properly on our computers and its functions.  We were also told we
    needed to do a specification of the idea we had come up with.
    Once the meeting was over we started coding as a group some basic
    test classes to look into how the controls could work for our
    game.  – 4 hours
  \item \textbf{Dxs970, Dwc928, mxs968, jkx988}\\
    WE all went away and worked upon our specification.
  \item \textbf{Dxs970}\\ Typed up the week’s notes that we made
    during the meetings. – 30 min
  \item \textbf{Mxs968}\\
    Worked more on the test classes that were made during the team
    meetings, fixing bugs and making it overall better.
  \end{itemize}
\item \textbf{Week 3}
  \begin{itemize}
  \item On Tuesday we again met up worked together as a team and
    started to build up the abstract classes that will be used to make
    the base game. – 2 hours We had our usual tutor meeting on the
    Thursday which we discussed the progress of the project and talked
    about the specifications we made with Errol.  Afterwards we coded
    together for a few hours, continuing to work on the abstract
    classes and expanding a few of them . – 3 hours
  \item \textbf{Dxs970}\\
    Added code to the test class to include mouse listeners so we
    could test the capabilities of using the mouse with the game. – 1
    hour 30 min Typed up weekly documentation from meetings. – 30 min
    Tried to work on the control class and the classes it needed to be
    added to but found it didn’t want to be added to the panel class
    so tried to work around it. – 1 hour
  \item \textbf{Dwc928}\\
    Worked on the paint methods in the GamePanel.
  \item \textbf{Jxk988}\\
    I mostly just planned the classes that was set to do in the
    meeting, then added the the functionality they were going to
    require.
  \item \textbf{Mxs968} Worked on creating some pruning methods for
    the arrays that were in the game class Wrote a few J unit tests to
    get use to the testing system
  \end{itemize}
\item \textbf{Week 4}
  \begin{itemize}
  \item Carried on working on the controls and found I could only get
    the frame to work properly with the class I wrote so went with
    using that for now. – 1 hour Had our weekly meeting and discussed
    the progress of the game – 1 hour Worked with the group to decide
    on the weekly task split up – 30 min
  \item \textbf{Dxs970}\\, mxs968 Discussed together on how
    projectiles will be handed and did some pair programming.
  \item \textbf{Dxs970}\\
    Carried on working on the controls but ran into problems with the
    frame so did a work around to make it work properly with the class
    that was there. – 1 hour
  \item \textbf{Dwc928}\\
    Worked on the GamePanel and Unit Classes
  \item \textbf{Jxk988}\\
    Worked on the abstract super classes and continued to expand upon
    them.  Mainly focused upon the projectile and weapon classes.
  \item \textbf{Mxs968} Worked upon the super classes that Jere had
    done for projectiles and unit by adding in methods such as do move
    and fixing bugs.
  \end{itemize}
\item \textbf{Week 5}
  \begin{itemize}
  \item Had the weekly meeting with the tutor which involved him
    looking over our tests and giving feedback on them – 1 hour After
    the meeting we decided upon the weekly task split – 30 min
  \item \textbf{Dxs970}\\
    Started working on Test classes for the demonstration that was on
    Thursday – 1 hour Worked on the control classes again to improve
    functionality and also fix bugs -1hour 30 min Tried to fix up the
    game (make it redraw again etc) since changes we made in the week
    broke it – 2 hours
  \item \textbf{Dwc928}\\
    Wrote Player and Enemy test classes Tried and failed to write a
    test class for the controls class
  \item \textbf{Jxk988}\\
    Wrote the JUnit tests for all the classes that he had worked on.
  \item \textbf{Mxs968} Worked on improving test classes Worked on
    fixing bugs with the panel class
  \end{itemize}
\item \textbf{Week 6}
  \begin{itemize}
  \item Met up on Tuesday to code together and work out some bugs in
    the code – 3 hours Had the weekly meeting and demonstrated the
    code – 1 hour Worked on things talked about in the demonstration
    such as adding a timer and logic loop– 1 hour Decided upon the
    weekly break down – 30 min
  \item \textbf{Dwc928, mxs968}\\ Talked together about how to best
    implement the spawn class and its functions
  \item \textbf{Dxs970}\\
    Started working on the projectiles to get a working game for the
    demonstration -1 hour Got the basic projectile class working – 1
    hour
  \item \textbf{Dwc928}\\
    Created theSpawn class to create static enemies Made adjustments
    to BasicFrame and GamePanelclasses to incorporate the spawn class.
    Wrote a SpawnTest class which needs modifying due to changes.
  \item \textbf{Jxk988}\\
    Went through the existing code and cleaned it a bit.  Separated
    the frame’s code into three parts: initialization, logic and
    rendering.  Implemented a timer for the game, so that it would run
    at 60 FPS.
  \item \textbf{Mxs968} Added a spawns array to the game class.
    Started work on collision detection.
  \end{itemize}
\item \textbf{Week 7}
  \begin{itemize}
  \item Had the tutor meeting and showed him the current code state –
    30 min Fixed projectiles fully – 1 hour
  \item \textbf{Dxs970}\\
    Worked on converting projectiles over to the complex type but had
    problems with it detecting the shapes being used – 2 hours Worked
    on a workaround to fix the projectile problem which fixed it. – 1
    hour
  \item \textbf{Dwc928}\\
    Made modifications in the Spawn class to spawn enemy objects at
    fixed points which is better than randomly.  Started to think
    about the documentation and researched what to include.
  \item \textbf{Jxk988}\\
    I created the background for the game, to give it the illusion
    that you are moving somewhere. It
  \item \textbf{Mxs968} Worked on researching on when to spawn enemies
    in the game loop Wrote a path super class and straight path class
    for enemies and projectiles to use.  Started working on some basic
    networking base code.
  \end{itemize}
\item \textbf{Week 8}
  \begin{itemize}
  \item Had weekly team meeting on Thursday and talked about a few of
    the problems we were having.
  \item \textbf{Dxs970}\\,\item \textbf{Mxs968} Discussed networking
    and the problems that were appearing– 1 hour
  \item \textbf{Dxs970}\\
    Worked on some projectile paths – 1 hours
  \item \textbf{Dwc928}\\
    Plan to document parts of the final report later in the week
  \item \textbf{Jxk988}\\
    Started making sprites for the ships and projectiles with the help
    of a friend Implemented the graphics into the game.
  \item \textbf{Mxs968} Worked on a basic menu and pause function of
    the game Worked a lot on the networking of the game trying to get
    it to function right.
  \end{itemize}



\item \textbf{Week 9}
  \begin{itemize}
  \item Had the weekly team meeting where we discussed solutions to
    the networking problems with the tutor.  We talked over the
    current development state of the game.
  \item \textbf{Dxs970}\\
    Started work on the menu base code for switching out panels Fixed
    control issues that were going on.
  \item \textbf{Dwc928}\\
    Started the report using LaTex template Documented most of the
    requirements definitions
  \item \textbf{Jxk988}\\
    Created a fancier mainmenu to use.
  \end{itemize}
\item \textbf{Week 10}
  \begin{itemize}
  \item Met up a few hours before the demonstration to fix any bugs we
    could before it started Had our team demonstration.
  \item \textbf{Mxs968},dxs970 Worked together to solve the panel
    switching issues using threads.
  \item \textbf{Dxs970}\\
    Worked a lot more on trying to fix the card switching on the menu
    Tried to fix the game not pausing when escape was pressed.
  \item \textbf{Dwc928}\\
    Started to document the design section of the report
  \item \textbf{Jxk988}\\
  \item \textbf{Mxs968} Got the networking to work properly
  \end{itemize}
\item \textbf{Week 11} 
  \begin{itemize}
  \item We all worked on the report
  \end{itemize}
\end{itemize}
